Reproduction of Civic Honesty around the Globe

### 2021-03-23 outputs/paper/paper.Rmd
Update paper.Rmd

@@

## Description of Study

## Methodology and Data Collection

## Power Analysis
```{r, echo = FALSE, message = FALSE}
dfPwr <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1)

>>>>

## Cost
The wallets for the money condition contained the equivalent of US $13.45, and the ones for the big money condition contained the equivalent of US $94.15 [@citeCohn]. So, the total amount of the cash spent for the experiment was $249,000, including exchange fees. Additionally, $3,600 was spent for the production of the wallets: $1,000 for printing business cards, $800 for producing plastic wallets, and $1,800 for copying keys. The research assistants were paid an hourly wage of $25 per hour, and the total wage expense was $300,000. The total expenditure on transportation such as flights and car rentals was $150,000.

## Power Analysis
We ran power analysis to check whether the research team used an appropriate sample size for the original paper. Firstly, we calculated the proportions of the returned wallets in the control group (the ‘no money’ condition) and the treatment group (‘the ‘money’ condition), using the raw data using the dplyr’s select, group_by, summarise, and mutate functions [@citeDplyr]. Then, we calculated the effect size, using the formula written by Stephane Champely [@citePwrPdf]. Lastly, we ran the two-sample test for proportions to estimate the required sample size which is required to show a significant difference between the two groups, using the ‘pwr’ package [@citePwr]. The result of the test shows that the most appropriate size of a sample to compare the two condition groups is 313 for each. Since the sample size of the control group is 7,888 and that of the treatment group is 8,211, we can say that the sample size is large enough to find a statistically significant difference between the two groups. The result of the power analysis is displayed below.

```{r, include = FALSE, message = FALSE}
dfPwr <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1)

@@
